---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{r}
library(tidyverse)

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRHaMrOqii2tFpTH9s4SEv7Wv1PNuF7fwck5SOM9F2pXzyNibgYcm4KyM9qoM3O0jDUcoFIKnN7K4gF/pub?output=csv")

# Renaming columns
latest_data <- logged_data %>%
  rename(
    timestamp = `Timestamp`,
    campus = `UoA or AUT Campus?`,
    building_num = `What was the building number of the observation? (Enter answer without B, i.e., for building 110N, don't use B110N, use 110N) Link to map for convenience.`,
    building_name = `What was the building name of the observation? (Use capitals) Link to map for convenience.`,
    time = `What was the time of the observation?`,
    date = `What was the date of the observation?`,
    quantity = `Quantity of same brand seen in the location? (e.g., 2 at one table)`,
    brand = `What was the brand of the drink?`
  )

# Summary values
min_quantity <- min(latest_data$quantity, na.rm = TRUE)
max_quantity <- max(latest_data$quantity, na.rm = TRUE)
mean_quantity <- mean(latest_data$quantity, na.rm = TRUE)
median_quantity <- median(latest_data$quantity, na.rm = TRUE)
mode_quantity <- names(which.max(table(latest_data$quantity)))
num_rows <- nrow(latest_data)
earliest_date <- min(latest_data$date, na.rm = TRUE)
latest_date <- max(latest_data$date, na.rm = TRUE)
most_common_brand <- names(which.max(table(latest_data$brand)))
most_common_campus <- names(which.max(table(latest_data$campus)))
```

```{css}
body {
  font-family: "Arial", sans-serif;
  text-align: center;             /* Center all text */
  background-color: #f9f9f9;      /* Soft light background */
  color: #333;                     /* Dark text for readability */
  line-height: 1.6;                /* Better spacing */
  margin: 20px;
}
h1, h2, h3 {
  text-align: center;              /* Center headings */
  color: #2a9d8f;                  /* Teal headings */
  text-shadow: 1px 1px 2px #ccc;   /* Subtle shadow for 3D effect */
}
h2 {
  font-size: 2.5em;
  margin-bottom: 0.5em;
}
h3 {
  font-size: 1.5em;
  margin-top: 0.8em;
}
img {
  border: 2px solid #2a9d8f;  /* add border around the plot */
  border-radius: 15px; 
  max-width: 80%;              /* scale the plot */
  transition: transform 0.3s ease, box-shadow 0.3s ease; /* Smooth hover */
  display: block;
  margin: 0 auto;              /* center the plot */
  box-shadow: 3px 3px 6px #aaa; /* add shadow */
}
img:hover {
  transform: translateY(-10px) scale(1.02); /* Move up slightly and grow */
  box-shadow: 5px 5px 15px rgba(0,0,0,0.3); /* Shadow becomes stronger */
  cursor: pointer;                       /* Optional: pointer to indicate interaction */
}
p {
  font-size: 1.1em;
  margin: 0.8em auto;
  max-width: 700px;                /* Limit width for readability */
}
```

## Energy Drink Observations

This dynamic report takes a look at the observations collected from our Google Form collected across 2 campuses, UoA and AUT. It tracks how many drinks were observed, what brand they were, date, and campus.

### Summary of Observations

There were a total of `r num_rows` energy drink observations recorded.

The earliest observation was on `r earliest_date` and the latest observation was on `r latest_date`.

## Bar Charts

```{r}
ggplot(latest_data, aes(x = brand)) +
  geom_bar(fill = "skyblue") +
  labs(title = "Brand Distribution of Energy Drinks",
       x = "Brand",
       y = "Count") +
  theme_minimal()
```

The brand most frequently observed was `r most_common_brand`.

```{r}
ggplot(latest_data, aes(x = campus)) +
  geom_bar(fill = "skyblue") +
  labs(title = "Distribution of Campus Observations",
       x = "Campus",
       y = "Number") +
  theme_minimal()
```

The campus with the higher proportion of observations is `r most_common_campus`.

```{r}
ggplot(latest_data, aes(x = quantity)) +
  geom_bar(fill = "skyblue") +
  labs(title = "Number of Energy Drinks per Observation",
       x = "Quantity",
       y = "Amount") +
  theme_minimal()
```

The most frequently observed number of drinks per observation was `r mode_quantity`.



